On the presentation of orthogonal groups over polynomial rings

### 2019-07-31 dl-paper.tex
Minor fix

\subsection{Construction of a model for $\St(\Phi, M[X] + A[X^{-1}])$}
Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
Let $A$ be a local ring with maximal ideal $M$.
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$. If we set $t = X^{-1}$, the notation of the present subsection becomes consistent with that of~\cref{sec:presentation}.

@@

  Let us verify the second assertion...
\end{proof}

>>>>

\subsection{Construction of a model for $\St(\Phi, M[X] + A[X^{-1}])$}
Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
Let $A$ be a local ring with maximal ideal $M$.
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$. The notation of the present subsection is consistent with~\cref{sec:presentation} if we set $t = X^{-1}$, $I = M$.

@@

  The second assertion can be verified directly using~\eqref{T_1}, \eqref{T_leq0} and the fact that $\St(\Phi, A[X\inv])$ is generated by $x_\alpha(a)$ and $x_\alpha(aX\inv)$ for $\alpha\in\Phi$, $a\in A$.
\end{proof}

We need to verify the following property: for $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$. It suffices to verify this for $g = z_\alpha(f, \xi)$, $f \in M[X]$, $\xi\in A[X]$.
